\section{Literatura}

\begin{thebibliography}
    \raggedright
\bibitem{msrc} 
    MSRC, “A proactive approach to more secure code | MSRC Blog | 
    Microsoft Security Response Center,” Microsoft.com, Jul. 16, 2019. 
    \url{https://msrc.microsoft.com/blog/2019/07/a-proactive-approach-to-more-secure-code/} 
    (pristupljeno Sep. 08, 2024).

    \bibitem{parsing} 
    “Parsing” Rochester.edu, 2024.
    \url{https://www.cs.rochester.edu/u/nelson/courses/csc_173/grammars/parsing.html#:~:text=Recursive%2Ddescent%20parsing%20is%20one,non%2Dterminal%20with%20a%20procedure} 
    (pristupljeno Sep. 21, 2024).

    \bibitem{dragonbook} 
    A. V. Aho, M. S. Lam, R. Sethi, and J. D. Ullman, \emph{Compilers: Principles, Techniques, and Tools}, 2nd ed. Boston, MA, USA: Addison-Wesley, 2006.

    \bibitem{rust-guide} 
    “Getting Started - Rust Compiler Development Guide,” Rust-lang.org, 2024. 
    \url{https://rustc-dev-guide.rust-lang.org/getting-started.html} (pristupljeno Sep. 28, 2024).

    \bibitem{rust-reference}
    “Introduction - The Rust Reference,” Rust-lang.org, 2015. 
    \url{https://doc.rust-lang.org/reference/introduction.html} (pristupljeno Sep. 29, 2024).
    
    \bibitem{rustonomicon}
    “Meet Safe and Unsafe - The Rustonomicon,” Rust-lang.org, 2024. 
    \url{https://doc.rust-lang.org/nomicon/meet-safe-and-unsafe.html} (pristupljeno Sep. 29, 2024).

    \bibitem{editions}
    “What are editions? - The Rust Edition Guide,” Rust-lang.org, 2024.
    \url{https://doc.rust-lang.org/edition-guide/editions/} (pristupljeno Okt. 03, 2024).

    \bibitem{unstable}
    “The Unstable Book - The Rust Unstable Book,” Rust-lang.org, 2024. 
    \url{https://doc.rust-lang.org/unstable-book/index.html} (pristupljeno Okt. 06, 2024).

    \bibitem{unstable-flagsunstable}
    Li, Chenghao, et al. “Demystifying Compiler Unstable Feature Usage and Impacts in the Rust Ecosystem.” 26 Oct. 2023. arXiv, Pristupljeno 6 Oct. 2024. 

    \bibitem{rust-language}
    Bugden W, Alahmar A. Rust: The programming language for safety and performance. arXiv preprint arXiv:2206.05503. 2022 Jun 11.

    \bibitem{supply-chain}
    P. Mainardi, “The Rising Threat of Software Supply Chain Attacks: Managing Dependencies of Open Source projects,” Linuxfoundation.eu, Aug. 15, 2023.
    \url{https://linuxfoundation.eu/newsroom/the-rising-threat-of-software-supply-chain-attacks-managing-dependencies-of-open-source-projects} (pristupljeno Okt. 20, 2024).

    \bibitem{oss-architecture}
    “The Architecture of Open Source Applications (Volume 1)LLVM,” Aosabook.org, 2024. 
    \url{https://aosabook.org/en/v1/llvm.html} (pristupljeno Nov. 04, 2024).

    \bibitem{llvm}
    “The LLVM Compiler Infrastructure Project,” Llvm.org, 2024. 
    \url{https://llvm.org/} (pristupljeno Nov. 04, 2024).
\end{thebibliography}